\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   
   Social networks come gaining a big highlight between the society in present times. Each day, new networks are developed, deserving the attention of several users in all the world. It becomes necessary developing a tool that assists developers create new networks in a way faster and practical, without not worry with recurring problems in this type of system. In order to collaborate with this technological context, this work proposes developing a framework to provide common resources in social networks development, for example, the users relationship. In this way, this proposal seeks create the relationship logic between users in a virtual social network. It is also intended that this logic be extended and used in applications that instantiate the proposed support, in case, possibly, a framework. Beyond this resource, the framework implements some extra resources. This resources will be for domains schedulers and routes. In this way, a developer who uses the presented framework, will be available this resources, allowing apply as needed in a social network, without, necessarily, not worry with the implemented logic. Such support, which transcends most basic social network resources, seeks to meet users profiles, interested in most specific soccial networks. This scenario has become something desired in present times.

   \vspace{\onelineskip}
 
   \noindent 
   \textbf{Key-words}: Framework. Software reuse. Social Network. Graphs.
 \end{otherlanguage*}
\end{resumo}
